### 2015-11-14 TeachingStatement/main.tex
Fixes from Charles' suggestions

\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}

@@

%\linespread{2.5}
\begin{document}
\thispagestyle{empty}

@@

\section{Moderate Class Sizes}
Due to my previous success as a Lab Instructor, I was offered a
position as Lead Instructor for the second level undergraduate
programming course. This class is designed to introduce the students,
who learn Python in the first semester, to C++11. They learn
everything from basic syntax and STL tools to templates and how
to building their own data structures with dynamic memory.
I was given full autonomy to create course content, including
lectures, assignments, and assessments. To help with grading
assignments and lab work created by the 37 students, the
department assignment me two Lab Instructors.
I am proud to report that I received an average
of 3.81 out of 4 in post course student assessment.

In order to create an inclusive environment, I worked to
show my concern for each student’s understanding. While
lecturing I frequently paused and prompted for questions,
and did my best to gauge whether students were understanding
the material. This would often result in me changing the pace
of the lecture to meet the students’ comprehension, either
skipping slides or moving to the chalkboard to give further
examples. For those students who did not want to ask questions
in class, I utilized Piazza, an online tool where students
can post their questions anonymously. These questions could be
visible to everyone in the class, allowing students to answer
each other's’ questions, or only visible only to me.

@@

\section{Large Class sizes}
While my primary experiences have been with moderately sized
classes (25-50 students), I have taught a few lectures to much
larger classes (120+). Lectures of that size make it much more
difficult to interactively gauge student comprehension, making
alternative teaching tools all the more important. The small
group worksheet approach became even more critical as, unlike
the lecture, it is unaffected by class size. It also provided
me an opportunity to work with small groups of students to
answer specific questions or to clarify ideas, something impossible
during large scale lecture. As a teaching assistant in these
courses I saw the effectiveness of video tutorials and online
classroom management systems which allow students to work together to answer each other’s questions.

@@

\section{Outreach}
During my masters I was the chair of an ACM SIG set up to organize
the MegaMinerAI programming competition each semester.
In this competition small teams of students are given
24 hours to write programs which act as the player in a computer game.
These programs compete with those written by other students,
with the results visualized. The competition focuses on making
it as easy as possible to write useful AIs, and making the game
as visually interpretable as possible. These goals help create
a community building challenge which is open to creativity and
translates student’s work into visual improvement.
The competition saw a significant growth in participation under
my direction, with nearly 100 competitors from a department of
only 400 students. For my work with the organization the department
awarded me “Leader of the Year.”

>>>>

\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{verbatim}

@@

\usepackage{enumitem}
\setlist[itemize,enumerate]{noitemsep,nolistsep}
%\linespread{2.5}
\begin{document}
\thispagestyle{empty}

@@

\section{Quotations from Student Evaluations}
\begin{itemize}
\item ``Brian is a great TA. I consistently attended the labs because I was always learning and benefiting.''
\item ``Brian was always very helpful and also found a way to make you figure out what you were doing on your own.''
\item ``Often explained things that were confusing in an easy way to understand.''
\end{itemize}

\section{Teaching Classes of Moderate Size}
Due to my previous success as a Lab Instructor, I was offered a
position as Lead Instructor for the second level undergraduate
programming course. This class is designed to introduce the students,
who learn Python in the first semester, to C++11. They learn
everything from basic syntax and STL tools to templates and how
to building their own data structures with dynamic memory.
I was given full autonomy to create course content, including
lectures, assignments, and assessments. To help with grading
assignments and lab work created by the 37 students, the
department assignment me two Lab Instructors.
I am proud to report that I received an average
of 3.81 out of 4 in post course student assessment.

In order to create an inclusive environment, I worked to
show my concern for each student's understanding. While
lecturing I frequently paused and prompted for questions,
and did my best to gauge whether students were understanding
the material. This would often result in me changing the pace
of the lecture to meet the students' comprehension, either
skipping slides or moving to the chalkboard to give further
examples. For those students who did not want to ask questions
in class, I utilized Piazza, an online tool where students
can post their questions anonymously. These questions could be
visible to everyone in the class, allowing students to answer
each others' questions, or only visible only to me.

@@

\section{Teaching Classes of Large Size}
While my primary experiences have been with moderately sized
classes (25-50 students), I have taught a few lectures to much
larger classes (120+). Lectures of that size make it much more
difficult to interactively gauge student comprehension, making
alternative teaching tools all the more important. The small
group worksheet approach became even more critical as, unlike
the lecture, it is unaffected by class size. It also provided
me an opportunity to work with small groups of students to
answer specific questions or to clarify ideas, something impossible
during large scale lecture. As a teaching assistant in these
courses I saw the effectiveness of video tutorials and online
classroom management systems which allow students to work together to answer each other's questions.

@@

\begin{comment}
\section{Outreach}
During my masters I was the chair of an ACM SIG set up to organize
the MegaMinerAI programming competition each semester.
In this competition small teams of students are given
24 hours to write programs which act as the player in a computer game.
These programs compete with those written by other students,
with the results visualized. The competition focuses on making
it as easy as possible to write useful AIs, and making the game
as visually interpretable as possible. These goals help create
a community building challenge which is open to creativity and
translates student's work into visual improvement.
The competition saw a significant growth in participation under
my direction, with nearly 100 competitors from a department of
only 400 students. For my work with the organization the department
awarded me “Leader of the Year.”
\end{comment}
